---
title: "\\vspace{30pt} \\Huge Carnet de Sorties"
author: "\\Large Jeremy Zuchuat"
header-includes:
  - \usepackage[utf8]{inputenc}	
  - \usepackage{geometry}
  - \usepackage[default]{raleway}
  - \usepackage[T1]{fontenc}
  - \usepackage{lmodern}
  - \usepackage{moresize}
  - \usepackage{fontawesome}
  - \usepackage{paracol}
  - \usepackage{fancyhdr}
  - \usepackage{graphicx}
  - \usepackage{color}
  - \usepackage{transparent}
  - \usepackage{tikz}	
  - \usetikzlibrary{shapes, backgrounds,mindmap, trees}
  - \usepackage{enumitem}
  - \usepackage{hyperref}
  - \usepackage{mdframed}
  - \usepackage{datetime}
  - \usepackage{lscape}
  - \geometry{margin=2.25cm}
  - \pagestyle{empty}
  - \setlength{\parindent}{0mm}
  - \definecolor{maincol}{RGB}{ 80, 110, 150 } # \definecolor{maincol}{RGB}{ 225, 0, 0 }
  - \definecolor{darkcol}{RGB}{ 70, 70, 70 }
  - \definecolor{lightcol}{RGB}{245,245,245}
  - \setitemize{label={\color{maincol}\faCheck}}
  - \include{Latex/graphical_element}
  - \usetikzlibrary{calc}
  - \usetikzlibrary{decorations.pathmorphing}
  - \newdateformat{monthyeardate}{%
  - \monthname[\THEMONTH], \THEYEAR}
output: 
  pdf_document:
    keep_tex: true
---

\columnratio{0.4}
\setlength{\columnsep}{2.2em}
\setlength{\columnseprule}{4pt}
\colseprulecolor{lightcol}
\linespread{1.20}

```{r setup, include=FALSE}
  rm(list=ls())

  # Packages 
  library(readxl)
  library(rmarkdown)
  library(raster)
  library(rasterVis)
  library(rgdal)
  library(ggplot2)
  library(rasterpdf)
  library(grImport)
  library(plotKML)
  library(geosphere)

  knitr::opts_chunk$set(echo = TRUE)
```

\thispagestyle{empty}

\begin{tikzpicture}[overlay,remember picture]
	\draw [line width=0.3mm,decorate]
	($ (current page.north west) + (2.35cm,-2.35cm) $)
	rectangle
	($ (current page.south east) + (-2.35cm,2.35cm) $);
	\draw [line width=0.5mm,decorate]
	($ (current page.north west) + (2.5cm,-2.5cm) $)
	rectangle
	($ (current page.south east) + (-2.5cm,2.5cm) $);
\end{tikzpicture}

\begin{figure}
  \vspace{-20pt}
	\begin{center}
	\includegraphics[width=11cm]{Pictures/Cover.jpg}
	\end{center}
	\vspace{20pt}
\end{figure}

\begin{center} 
  \Large \monthyeardate\today
\end{center} 

\clearpage

\pagenumbering{arabic}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\cfoot{- \thepage -}

```{r info_touring, include=FALSE}

  # Working directory
  path_root <- "/Users/j.zuchuat/Documents/GitHub/JeremyZuchuat.github.io/map" 
  path_HTML <- "../ski_touring_html"
  path_GPX <- paste(path_root,"/gpx/simplified/",sep="") 
  
  # Main path
  setwd(path_root)

  # Info on tours
  info_touring <- read.csv("information/info_touring.csv",sep=",")

  # List GPX files
  list_GPX <- list.files(path = path_GPX)
  list_GPX <- list_GPX[substr(list_GPX,nchar(list_GPX)-3,nchar(list_GPX)) == ".gpx"]
  list_GPX <- substr(list_GPX,1,nchar(list_GPX)-4)
  
  # Palette raster
  pal <- colorRampPalette(c(rgb(0.1,0.1,0.1),rgb(1,1,1)))
  
  # Printing only two decimals
  print_decimal <- function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
  
  # Function status 
  print_status <- function(x) {
    message(x)
}
```

Hello